A formal approach but practical approach in train regulation

### 2025-06-23 paper/main.tex
Clarifier event handlers

For the sake of clarity $\handlerOf{E}{\tid{id}}$ denotes the list of handlers for events of train $\tid{id}$.

@@

The syntax of regulator programs is given by the non-terminal {\ttfamily stmt} in Grammar~\ref{gr:regulator_program}.
The program of the regulator is a set of rules, guarded by events. A rule $\ev{\tid{id}}{n}{A}$ denotes that upon entering the $n$-th block of its route, train $\tid{id}$ will trigger actions $A$. The list of actions in the handler are of four kinds: 
\begin{description}
	\item[\incr{\bid{id}}:] this updates the token $\bid{id}$ in $T$:  $T \cdot \incr{\bid{id}}  \triangleq T[\bid{id} \leftarrow T(\bid{id})+1]$
	\item [\wait{\bid{id}}{i}:] ...\todo{}
	\item [\turn{\sid{id}}{s}:] this instructs the regulator to turn the switch $\sid{id}$ into the $s$ state: $\sigma\cdot\turn{\sid{id}}{s} = \sigma[\sid{id} \leftarrow s]$
	\item [auth:] ...\todo{}
\end{description}

>>>>

@@

Train events are handled by the regulator. Upon such events, the regulator can take actions such as turning a switch, allowing or blocking a train, etc.. The regulator is equipped with a routing program. This routing program contains, for each train, a list of handlers. For a given train, the first handler of the list is the set of actions that have to be executed on the train's first event, second handler for the second event, and so on.

Given a routing program $E$, $\handlerOf{E}{\tid{id}}$ is the list of handlers of train $\tid{id}$, $\head{\handlerOf{E}{\tid{id}}}$ is the handler of the first event for that train.

The syntax of each handler is given by the non-terminal {\ttfamily stmt} in Grammar~\ref{gr:regulator_program}.\todo{est-ce toujours nécessaire maintenant que les handlers sont dans un liste ?}
The program of the regulator is a set of rules, guarded by events. A rule $\ev{\tid{id}}{n}{A}$ denotes that upon entering the $n$-th block of its route, train $\tid{id}$ will trigger actions $A$. The list of actions in the handler are of four kinds: 
\begin{description}
	\item[\incr{\bid{id}}:] this updates the token $\bid{id}$ in $T$:  $T \cdot \incr{\bid{id}}  \triangleq T[\bid{id} \leftarrow T(\bid{id})+1]$
	\item [\wait{\bid{id}}{i}:] ...\todo{}
	\item [\turn{\sid{id}}{s}:] this instructs the regulator to turn the switch $\sid{id}$ into the $s$ state: $\sigma\cdot\turn{\sid{id}}{s} = \sigma[\sid{id} \leftarrow s]$
	\item [auth:] ...\todo{}
\end{description}
